Tensor anisotropy as a tracer of cosmic voids

### 2015-02-18 cosmic_voids.tex
first pass on the conclusions

Here we introduce a new algorithm to define voids over the continous
matter density or velocity distribution defined on a fixed and
homogeneous spatial grid.
The algorithm uses the results from two tensorial schemes used to
classify the cosmic web.
The first (the T-web) is based on the Hessian of the gravitational potential or
tidal tensor \citep{Hahn07, Forero09}. 
The second (the V-web) is based on the velocity shear tensor
\citep{Hoffman12}. 
Our procedure allows for a description of the internal structure
of voids that goes beyond a simple definition of a void as an
underdense region in the large-scale matter distribution.
The tidal and the shear tensors encode more information than the
density field as they trace the collapsing or expanding
nature of the matter field, which defines the dynamics of the Cosmic
Web.

@@

We also find that the V-Web scheme produces an over-abundance of small
voids compared to the resuls of the T-Web.
A large number of these small voids are embedded in overdense regions. 
They are visible in the middle panel of Figure \ref{fig:FA_field} as
tiny white bubbles located inside sheets.
The existence of these small voids can be explained by
dynamics of shell crossing in collapsing sheets. 
As matter colides into a sheet, in their symmetry plane one will
find crossing sheets that effectively give a positive divergence in
the velocity field, resulting in a void identification by the
V-Web algorithm. This has been already discussed in \citet{Hoffman12}.

@@

The velocity profiles show the expected correlation with the features
already observed in the density, most notably the radial velocity is
cero close to flat regions in the density profile and positive around
regions of increasing density with radius.

The Fractional Anisotropy profiles also show remarkable similarities,
(inside each class of subcompensated and overcompensated)
and a close correlation with the behaviour in the density and velocity
profiles. 
From these profiles it becomes clear that our choice to delimit an
overcompensated void coincides with a ridge in the fractional
anisotropy. For the subcompensated voids the void boundary is located
for regions with an average FA value of $\sim 0.7-0.8$.

Put together, the results for the radial profiles support the 
evidence for a universal density profile using smaller void sizes
than the ones probed by \cite{Hamaus14}.

>>>>

Here we introduce a new algorithm to define voids over the continous
matter density or velocity distribution defined on a fixed and
homogeneous spatial grid.
The algorithm uses the results from two tensorial schemes used to
classify the cosmic web.
The first (the T-Web) is based on the Hessian of the gravitational potential or
tidal tensor \citep{Hahn07, Forero09}. 
The second (the V-web) is based on the velocity shear tensor
\citep{Hoffman12}. 
Our procedure allows for a description of the internal structure
of voids that goes beyond a simple definition of a void as an
underdense region in the large-scale matter distribution.
The tidal and the shear tensors encode more information than the
density field as they trace the collapsing or expanding
nature of the matter field, which defines the dynamics of the Cosmic
Web.

@@

We also find that the V-Web scheme produces an over-abundance of small
voids compared to T-Web.
A large number of these small voids are embedded in overdense regions. 
They are visible in the middle panel of Figure \ref{fig:FA_field} as
tiny white bubbles located inside sheets.
The existence of these small voids can be explained by
dynamics of shell crossing in collapsing sheets as discussed in
\citet{Hoffman12}.    
The main argument is that as matter colides into a pancake-like
fashion crossing sheets encounter each other at the symmetry plane.
This effectively gives a positive divergence in the velocity
field, resulting in a void identification by the V-Web algorithm.

@@

The velocity profiles show the expected correlation with the features
already observed in the density, most notably the radial velocity goes to
zero close to flat regions in the density profile and is positive around
regions of increasing density with radius.

The Fractional Anisotropy profiles also show remarkable similarities,
(inside each class of subcompensated and overcompensated voids)
and a close correlation with the behaviour in the density and velocity
profiles. 
From these profiles it becomes clear that the limit of overcompensated
void coincides with a ridge in of FA values close to $0.9$. 
This value is close to the limit FA=$0.95$ we impose in the watershed
algorithm, indicating that these voids are very close to spherical.
For the subcompensated voids the FA quickly increases to FA values of 
$\sim 0.7-0.8$ at $r/r_{\rm eff}\sim 1$ to find a plateau, which is
quite far from the limiting FA$=0.95$ suggesting that these voids are
far from spherical.

Put together, the results for the radially averaged profiles support the 
evidence for a universal density profile.  
This extends the work done
by \cite{Hamaus14} to smaller void sizes.

The method we present here finds voids with reasonable properties
compared to different results published in the literature. 
This gives support to a new tracer, the Fractional Anisotropy, to be
used in the study of cosmic voids. 
Furthermore, the complementary physical picture in the two different
web finding algorithms opens the possibilities to make a joint
analysis of the tidal and dynamical structure of voids.
